Convolutional Neural Network to Detect Equivalent Questions in Online Forums \\ DL-IC 2018 Project

### 2018-07-03 paper/paper_final.tex
Revert "Merge branch 'master' of https://github.com/Lucascanna/deep-learning"
This reverts commit 04f6954c833d2317383692d0524e31ad34392c2c, reversing
changes made to cef2ebff6cd24ba221b8fcb90ad7830749a7868c.

%%%%%%%%% ABSTRACT
\begin{abstract}
   In the context of online forums, although two questions may seem very different in terms of vocabulary, length and syntax, they may eventually ask the same thing. In this work, we try to detect semantically equivalent questions using a simple Convolutional Neural Network (CNN). The proposed CNN generates distributed vector representations \cite{mikolov2013distributed} for pairs of questions and score them using a similarity metric. We evaluate in-domain \emph{word embeddings} versus the ones trained by Google using all the English Wikipedia \footnote{\url{http://nlp.stanford.edu/data/glove.6B.zip}}: in the former case, the experimental results are very close to the paper \cite{bogdanova2015detecting} we are trying to replicate, while in the latter case they are a bit worse. In particular, in-domain word embeddings do not bring any improvement to the performances as they do in the Bogdanova's work.
\end{abstract}

@@

In general, the results obtained by our implementation are very close to the ones of the replicated paper. The only shortcoming was that the in-domain word embeddings trained by us did not improve the performances as they did in Bogdnova et al.'s work. We think this is due to the fact that, since the paper does not provide any description of the model employed to train the domain-specific word-embedddings, it is very likely that our model is significantly different from the one they used.\\

@@

    Bogdanova et al. explicitly state that the different sizes of questions is one of the main challenges of their work. Nevertheless, they do not specify the way they solved this issue. We, therefore, tried to experiment two different solutions: fixing the length of each question to the \textbf{maximum} and the \textbf{mean} length of the questions.The second approach resulted to yield the greater accuracy.

@@

    The paper does not provide any information about the model used to train in-domain word embeddings. Therefore, we based our work on a very good tutorial \footnote{\url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}} on how to build a the \emph{word2vec} model \cite{mikolov2013distributed} in Keras. However, the experimental results concerning this aspect of our work were not very satisfactory.

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
   In the context of online forums, although two questions may seem very different in terms of vocabulary, length and syntax, they may eventually ask the same thing. In this work, we try to detect semantically equivalent questions using a simple Convolutional Neural Network (CNN). The proposed CNN generates distributed vector representations for pairs of questions and score them using a similarity metric. This work is the replication of \cite{bogdanova2015detecting}: we basically try to perform the same experiments and compare our results with theirs. The replication turned to be not straightforward since some crucial implementation details are missing in the Bogdanova et al.'s description. Hence, we have found quite stimulating to replicate this paper filling the holes with our own ideas. In particular, our efforts focused mainly on the following three aspects that were not explicitly treated in the paper: unequal text length, the type of convolution and the training of in-domain word embeddings. The final results we obtained are quite close to the our target; whereas the optimal parameters values of the network are quite different from \cite{bogdanova2015detecting}.
\end{abstract}

@@

In general, the results obtained by our implementation are very close to the ones of the replicated paper. Surprisingly, as we will discuss in Section 4, the main differences in the results are about the optimal hyper-parameter values of the network.\\

@@

    Bogdanova et al. explicitly state that the different sizes of questions is one of the main challenges of their work. Nevertheless, they do not specify the way they solved this issue. We, therefore, tried to fix the length of each question to the \textbf{maximum} and to the \textbf{mean} length of all the questions. The first approach resulted to yield the greater accuracy.

@@

    The paper does not provide any information about the model used to train in-domain word embeddings. Initially, we tried to build our own \emph{word2vec} model \cite{mikolov2013distributed} to generate word-embeddings using as training data the same dataset used to train the main network \footnote{To do so we followed this good tutorial: \url{http://adventuresinmachinelearning.com/word2vec-keras-tutorial/}}. However, the training of this network turned out to be very slow and resulting embeddings perfomed poorly. \\
    We, then, decided to use Gensim, a very simple library which generates word-embeddings given the training data. The resulting embeddings performed very well, allowing the main network to achieve up to 90\% of accuracy on the validation set.
